### 2017-10-04 TF-vldb2018/full/sec-appendix.tex

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball([v, r])$.\\
{\sl Output:\/} The perfect subgraph $G_s$ of $\ball{[v,r]}$ \wrt $P$.\\
\sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
\icc \>\hspace{2ex}\= $\matchs(u)$ := \{$w | w$ is in $\ball{[v, r]}$ and $l_P(u)\in l(w)$\};\\
\icc \> \While there are changes \Do\\
\icc \>\> \For each edge ($u, u'$) in $E_P$ and each node $w \in \matchs(u)$ \Do\\
\icc \>\>\hspace{2ex}\= \If there is no edge ($w, w'$) in $\ball{[v, r]}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
\icc \> \If there exists $|\matchs(u)|\not\in f_{P}(u)$ \Then \Return $\emptyset$;\\
\icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> Construct the perfect subgraph $G_s$ \wrt $\Reps$;\\
\icc \> \Return $G_s$;\\
}

@@

As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
\rgraphsim finds the perfect subgraph of $P$ and $\ball{[v, r]}$.
For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
and then removes nodes from $\matchs(u)$ iteratively (lines 3-6).
A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
Finally, it checks whether the capacity bound on each node $u$ is satisfied (line 7).
If so, \rgraphsim constructs the perfect subgraph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 9-10).

>>>>

\vspace{-2ex}
\begin{figure}[h!]
%\vspace{-2ex}
\begin{center}
{\small
\myhrule
\vspace{-2ex}
\mat{0ex}{
\sstab {\sl Input:\/} Pattern graph $P(V_{P}, E_{P})$ and ball $\ball{[v, r]}$.\\
{\sl Output:\/} The match graph $G_s$ for $P$ in $\ball{[v, r]}$ .\\
\sstab \bcc \hspace{1ex} \= \For each $u \in V_{P}$ \Do\\
\icc \>\hspace{2ex}\= $\matchs(u)$ := \{$w | w$ is in $\ball{[v, r]}$ and $l_P(u)\in l(w)$\};\\
\icc \> \While there are changes \Do\\
\icc \>\> \For each edge ($u, u'$) in $E_P$ and each node $w \in \matchs(u)$ \Do\\
\icc \>\>\hspace{2ex}\= \If there is no edge ($w, w'$) in $\ball{[v, r]}$ with $w' \in \matchs(u')$ \Then\\
\icc \>\>\>\hspace{2ex}\= $\matchs(u)$ := $\matchs(u) \setminus \{w\}$;\\
\icc \>\> \If $\matchs(u)$ = $\emptyset$ \Then \Return $\emptyset$;\\
\icc \> $\Reps$ := \{$(u,w) | u \in V_{P}, w \in \matchs(u)$\};\\
\icc \> Construct the match graph $G_s$ \wrt $\Reps$;\\
\icc \> \Return $G_s$;\\
}

@@

As shown in Fig~\ref{alg-rsim}, given $P$ and ball $\ball{[v, r]}$,
\rgraphsim finds the match graph for $P$ in $\ball{[v, r]}$.
For each node $u$ in $V_{P}$, it first computes the set $\matchs(u)$ of candidate matches $w$ containing the label of $u$ (lines 1-2),
and then removes nodes from $\matchs(u)$ iteratively (lines 3-7).
A node $w$ is removed from $\matchs(u)$ if there is a adjacent node $u'$ of $u$,
but there exists no adjacent node $w'$ of $w$ such that $w'\in \matchs(u')$.
If so, \rgraphsim constructs the match graph $G_s$ \wrt the maximum match relation $\Reps$ and returns it (lines 8-10).

### 2017-10-04 TF-vldb2018/full/sec-expt.tex

\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.

@@

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi}
\includegraphics[scale=0.38]{./fig/union-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying Datasets}]{\label{fig-exp-extraspace}
\includegraphics[scale=0.38]{./fig/union-space.eps}}
\vspace{-2ex}

\end{center}
\vspace{-3ex}
\caption{Performance evaluation of algorithm \inc for dynamic top-$k$ team formation (Cit: \citationd, Syn: \synthetic)}
\label{exp-inc}
%\end{widepage}
\vspace{-3ex}
\end{figure*}

@@

We find the following.
(1) \inc outperforms \optgrouprec when insertions are no more than 28\% and 32\% on \citationd and \synthetic (resp. 40.5\% and 45\% for deletions).
%When the changes are 16\% for insertions (resp. 20\% for deletions), \optinc improves \optgrouprec by over 42\% and 24\% (resp. 70\% and 91\%).
(2) For the same $|\Delta G|$, \inc needs less time to process deletions than insertions.
(3) We have conducted a survey: the user increment on Facebook~\cite{facebookStat} and Twitter~\cite{twitterStat} daily reaches 1.23\textperthousand\ and 2.47\textperthousand.
Therefore, \inc is able to handle the increments accumulated in dozens of days on Facebook and Twitter
at a high efficiency.
(4) \inc outperforms \optgrouprec when hybrid data updates are no more than 32\% and 36\% on \citationd and \synthetic respectively.

@@

\stitle{Exp-5: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-extraspace}, the incremental algorithm \inc takes (25MB, 130MB) extra space to store all its auxiliary structures on (\citationd, \synthetic), which need (36MB, 482MB) space to store themselves.
That is, the auxiliary structures are light-weight, and only take (69.4\%, 26.9\%) extra space compared with the original datasets.

@@

\sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
\eg it took 116s when $|V|=1.39M$ and $|V_P|=10$.

>>>>

\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship, and generated 200 labels based on phrase clustering of paper titles.

@@

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF, (2) incremental algorithm \inc for \dynteamF,
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}, which is firstly proposed for the team formation problem,
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}, and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Most of the algorithms for \teamF, including  \mindia and \denalk, only compute the best team,
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure \cite{Lawler1972}.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

%\hspace{-5.5ex}
\subfigure[{\scriptsize Varying $|\Delta P|$ in update sets}]{\label{fig-exp-patinc-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying $|\Delta G|$ in update sets}]{\label{fig-exp-datainc-multi}
\includegraphics[scale=0.38]{./fig/union-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Vary $(|\Delta P|,|\Delta G|)$ in update sets}\hspace{-8.5ex}]{\label{fig-exp-hyb-datapat-multi}
\includegraphics[scale=0.38]{./fig/union-pattern-data-multi.eps}}
\hspace{0.2ex}
\subfigure[{\scriptsize Varying Datasets}]{\label{fig-exp-extraspace}
\includegraphics[scale=0.38]{./fig/union-space.eps}}
\vspace{-2ex}
\end{center}
\vspace{-2.5ex}
\caption{Performance evaluation of algorithm \inc for dynamic top-$k$ team formation (Cit: \citationd, Syn: \synthetic)}
\label{exp-inc}
%\end{widepage}
\vspace{-2.5ex}
\end{figure*}

@@

We find the following.
(1) \inc outperforms \optgrouprec when insertions are no more than 28\% and 32\% on \citationd and \synthetic (resp. 40.5\% and 45\% for deletions).
%When the changes are 16\% for insertions (resp. 20\% for deletions), \optinc improves \optgrouprec by over 42\% and 24\% (resp. 70\% and 91\%).
(2) For the same $|\Delta G|$, \inc needs less time to process deletions than insertions.
(3) We have conducted a survey: the user increment on Facebook~\cite{facebookStat} and Twitter~\cite{twitterStat} daily reaches 1.23\textperthousand\ and 2.47\textperthousand.
Therefore, \inc is able to handle the increments accumulated in dozens of days on Facebook and Twitter
at a high efficiency.
(4) \inc outperforms \optgrouprec when hybrid data updates are no more than 32\% and 36\% on \citationd and \synthetic, respectively.

@@

\stitle{Exp-5: Physical storage of auxiliary structures}. As shown in Fig.~\ref{fig-exp-extraspace}, the incremental algorithm \inc takes (25MB, 130MB) extra space to store all its auxiliary structures on (\citationd, \synthetic), while they need (36MB, 482MB) space to store themselves.
That is, the auxiliary structures are light-weight, and only take (69.4\%, 26.9\%) extra space compared with the original datasets.

@@

\sstab(2) Our batch algorithm for  top-$k$ team formation is efficient,
\eg it only took 116s when $|V|=1.39M$ and $|V_P|=10$.
